---
title: "compare_blood_loops"
output: html_document
date: "2026-04-13"
```

```{r}
library(tidyverse)
library(ggalluvial)
```

```{r}

basedir='/Users/varshiniramanathan/Documents/HansenLab/blood_data/remapped'
files <- list.files(basedir, pattern = "merged_calls.*\\.txt$", full.names = TRUE)

# Read them all, keeping filename as dataset label
df_all_loops <- files %>%
  set_names() %>%
  map_dfr(~ read.table(.x, header = TRUE, stringsAsFactors = FALSE) %>%
            as_tibble() %>%
            mutate(dataset = basename(.x)),
          .id = "source") %>% select(-annotation1,-annotation2)

# If you want to track individual IDs across datasets:
df_wide_loops <- df_all_loops %>% select(-source) %>%
  pivot_wider(names_from = dataset, values_from = pair) %>% select(starts_with("merged"))

df_counts_loops <- df_wide_loops %>%
  count(across(everything()))

ggplot(df_counts_loops,
       aes(y = n, axis1 = merged_calls_125kb_q0.01_classes2.txt, axis2=merged_calls_125kb_q0.01_classes.txt, axis3=merged_calls_125kb_q0.01_classes_new.txt)) +
  geom_alluvium(aes(fill = merged_calls_125kb_q0.01_classes2.txt), width = 1/12) +
  geom_stratum(width = 1/12, fill = "black", color = "grey") +
  geom_label(stat = "stratum", aes(label = after_stat(stratum))) +
  scale_fill_brewer(type = "qual", palette = "Set3") +
  ggtitle("loop classes with differing enhancer annotation")
```

```{r}

basedir='/Users/varshiniramanathan/Documents/HansenLab/adipose_data'
files <- list.files(basedir, pattern = "adipose_classes_merged_anchors.*\\.txt$", full.names = TRUE)

# Read them all, keeping filename as dataset label
df_all <- files %>%
  set_names() %>%
  map_dfr(~ read.table(.x, header = TRUE, stringsAsFactors = FALSE) %>%
            as_tibble() %>%
            mutate(dataset = basename(.x)),
          .id = "source") %>% select(-strand)

# If you want to track individual IDs across datasets:
df_wide <- df_all %>% select(-source) %>%
  pivot_wider(names_from = dataset, values_from = annotation) %>% select(starts_with("adipose"))

df_counts <- df_wide %>%
  count(across(everything()))

ggplot(df_counts,
       aes(y = n, axis3 = adipose_classes_merged_anchors_0.10_v2.txt, axis2 = adipose_classes_merged_anchors_0.10.txt, axis1=adipose_classes_merged_anchors.txt)) +
  geom_alluvium(aes(fill = adipose_classes_merged_anchors.txt), width = 1/12) +
  geom_stratum(width = 1/12, fill = "black", color = "grey") +
  geom_label(stat = "stratum", aes(label = after_stat(stratum))) +
  scale_x_discrete(limits = c("original","thresh_0.10", "thresh_0.10_v2"), expand = c(.05, .05)) +
  scale_fill_brewer(type = "qual", palette = "Set1") +
  ggtitle("anchor classes with differing enhancer annotation")
```

```{r}
df_counts <- df_all %>%
  count(dataset, pair)
# Now df_all looks like:
# id   pair   dataset
# 1    A      file1.txt
# 2    B      file1.txt
# 1    B      file2.txt
# ...

# If you want to track individual IDs across datasets:
df_wide <- df_all %>%
  pivot_wider(names_from = dataset, values_from = pair)

# Step 3: back to long format, ordered by dataset
df_long <- df_wide %>%
  pivot_longer(cols = starts_with("adipose"),
               names_to = "dataset",
               values_to = "pair")
```

```
